Proposed Solution

### 2016-02-11 ICFP/formalism.tex
make which will change

That is, taking the following definitions:
\begin{flalign*}
\mathcal{T}& =\ \{ r\ \mid \\
  & \forall file \in \mathcal{C},\ r(file)\  \land\\
  & \exists file \in \mathcal{C},\ r(file) \text{ is non-trivial}\ \land \\
  & \text{ if } \neg r(userfile) \text{ then system crash} \} \\
\mathcal{L}& =\ \{ r\ \mid \\
  & \forall file \in \mathcal{C},\ r(file)\  \land\\
  & \exists file \in \mathcal{C},\ r(file) \text{ is non-trivial} \} \\
\mathcal{R}& =\ \{ r\ \mid \\
  & r \in \mathcal{L}\ \land\\
  & \neg r(userfile) \}&\\
\end{flalign*}

@@

\subsection{merge}
  Merging the sets of rules from two files to build a new set that is true over both files is the most difficult and important function a rule must implement.
  This is generally implemented as a filter over the union of the two set, but may vary slightly.
  The second predicate of formal specification states that the rule cannot conflict with other existing rules.
  \begin{align*}
  \text{merge }& Set1 \: Set2= \{r \mid \\
    & r \in \text{Set1} \cup \text{Set2}\ \land \\
    & \exists file\ \forall r' \in \text{Set1} \cup \text{Set2}, r(file) \land r'(file) \} \\
  \end{align*}

>>>>

For probablistic learing
$\mathcal{C'}$ = Incorrect Configuration File Learning Set\\

That is, taking the following definitions:
\begin{flalign*}
\mathcal{T}& =\ \{ r\ \mid \\
  & \forall file \in \mathcal{C},\ r(file)\ *  \land\\
  & \exists file \in \mathcal{C},\ r(file) \text{ is non-trivial}\ \land \\
  & \text{ if } \neg r(userfile) \text{ then system crash} \} \\
\mathcal{L}& =\ \{ r\ \mid \\
  & \forall file \in \mathcal{C},\ r(file)\  \land\\
  & \exists file \in \mathcal{C},\ r(file) \text{ is non-trivial} \} \\
\mathcal{R}& =\ \{ r\ \mid \\
  & r \in \mathcal{L}\ \land\\
  & \neg r(userfile) \}&\\
\end{flalign*}

@@

\subsection{merge}
  Merging the sets of rules from two files to build a new set that is true over both files is the most difficult and important function a rule must implement.
  This is generally implemented as a filter over the union of the two set, but may vary slightly.
  The second predicate of formal specification states that the rule cannot conflict with other existing rules.
  \begin{align*}
  \text{merge* }& Set1 \: Set2= \{r \mid \\
    & r \in \text{Set1} \cup \text{Set2}\ \land \\
    & \exists file\ \forall r' \in \text{Set1} \cup \text{Set2}, r(file) \land r'(file) \} \\
  \end{align*}
